---
title: "FishErIes Size and functional TYpe model (FEISTY) in R"
author: "Yixin Zhao, Ken H. Andersen, and Karline Soetaert"
date: " 2024"
output:
  pdf_document:
    latex_engine: pdflatex
    keep_tex: true
vignette: >
  %\VignetteIndexEntry{FishErIes Size and functional TYpe model (FEISTY) in R}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
bibliography: references.bib
link-citations: yes
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE) # for printing the examples
if (!require(FEISTY)) devtools::install_github("Kenhasteandersen/FEISTY@R-Package")
library(FEISTY)
palette("ggplot2")  # ggplot2-style palette
```

# Introduction
This vignette provides a comprehensive description of the model equations, parameters, and numerical implementation used in the **FEISTY** model system [@petrik2019bottom; @van2021emergent]. Further, it provides a few examples at the end.

# The FEISTY model

## Biomass dynamics

### Fish dynamics

The biomass of each size class of a functional type of fish ($B_i$,
gWW m$^{-2}$) changes over time ($t$) according to source and sink of
energy [@deRoos2008]:
\begin{equation}
\dfrac{dB_{i}}{dt} =  J_{\mathrm{in},i}  + (\nu_{i} - \rho_i -\mu_i)B_i - J_{\mathrm{out},i},
\end{equation}
where $\nu_{i}$ is the rate of available energy for growth and
reproduction, $\rho_i$ is the rate of reproduction, and $\mu_i$
(year$^{-1}$) is the total mortality rate. The size of fish increases as
a result of growth. The grown flux out of the current
size class enters the next size class (excluding the largest fish). The
growth flux out of a size class $i$ is 
\begin{equation}
J_{\mathrm{out},i} = \gamma_i B_i,
\end{equation}
where $\gamma_i$ is the growth rate (year$^{-1}$). The growth
flux to a size class includes two parts for the smallest fish and
other sizes, respectively: 
\begin{equation}
    J_{\mathrm{in},i} =
  \begin{cases}
\epsilon_r \left(  J_{\mathrm{out},n} + \sum\limits_i \rho_i B_i \right),      & \text{$ i=1 $} \\
     J_{\mathrm{out},i-1}, & \text{$ i > 1$} 
  \end{cases}
\end{equation} 
where $\epsilon_r$ is the reproduction efficiency. The flux
into the smallest fish class ($i=1$) is from the reproduction of each
size class of mature fish plus the growth flux out of the
largest fish class ($J_{\mathrm{out},n}$) because they cannot grow larger. For
larger fish ($i > 1$), the growth flux into the size class $i$ is
from the growth of the previous neighboring size class ($i-1$).

### Resource dynamics

The resource $i$ biomass evolves over time according to a chemostat-like
growth and consumption by predators, which is the default resource
dynamic mode in four internal setups [@petrik2019bottom;
@van2021emergent]:

\begin{equation}
\dfrac{dR_{i}}{dt} =  r(K_i - R_i ) - \mu_{\mathrm{p},i} R_i,
\end{equation}

where $R$ is the state variable of a resource, $K$ is the carrying capacity
(gWW m$^{-2}$), and $r$ is the growth rate which is a constant value
(1 year$^{-1}$). $\mu_{\mathrm{p}}$ represents the predation mortality on the
resource. Alternatively, we provide the logistic growth strategy for
resources:

\begin{equation}
\frac{dR_i}{dt}=r_i \cdot R_i \cdot (1-\frac{R_i}{K_i}) - \mu_{\mathrm{p},i} \cdot R_i,
\end{equation}
which can be set in `paramAddResource()` function.

## Physiological rates

There are three main biological rates based on the allometric scaling relationship of the body size: the
mass-specific maximum consumption rate $C_{max,i}$ (year$^{-1}$), the
mass-specific clearance rate $V_{i}$ (m$^{2}$ gWW$^{-1}$ year$^{-1}$), and the
mass-specific metabolic rate $M_i$ (year$^{-1}$):
\begin{equation}
C_{max,i} = k_{\mathrm{T},i} \cdot a_{c} \cdot m_{i}^{b_{c}}  \label{eq:maxconsump}
\end{equation}
\begin{equation}
V_{i} = k_{\mathrm{T},i} \cdot a_{e} \cdot m_{i}^{b_{e}}      \label{eq:clearance}
\end{equation}
\begin{equation}
M_i = k_{\mathrm{TM},i} \cdot a_{m} \cdot m_{i}^{b_{m}}       \label{eq:metabolism}
\end{equation}
Here $k_{\mathrm{T},i}$ and $k_{\mathrm{TM},i}$
are scaling factors of temperature effects of each size class (see Section **Temperature
effects**). $a_{c}$, $a_{e}$, and $a_{m}$ are factors for each
biological rate; $b_{c}$, $b_{e}$, and $b_{m}$ are exponents.
These biological rates determine the energy gained from predation and
costs due to basal metabolism (see Section **Energy budget**).\
In the code implementation, these basic biological rates of fish (without
temperature effects) are assigned by the `paramAddPhysiology()` function.
The temperature effects on biological rates are added subsequently (see
Section **Temperature effects**).

## Energy budget

For a given size of fish $m_i$, the mass-specific available energy for
growth or reproduction (rate) $\nu_{i}$ is the result of the
mass-specific energy from assimilated food (rate) minus the
mass-specific metabolic rate:
\begin{equation}
\nu_{i} = \epsilon_\alpha f_i C_{\mathrm{max},i} - M_i
\end{equation}
where $\epsilon_\alpha$ is the assimilation efficiency. The mass-specific
feeding level $f_i$ (dimensionless) describes how much food a predator
can eat relative to the maximum consumption capability, ranging from 0
to 1: 
\begin{equation}
f_{i} = \frac{E_{i}}{E_{i}+C_{\mathrm{max},i}}
\end{equation}
Therefore, the mass-specific consumption rate $f_i C_{\mathrm{max},i}$ is based on type II
functional response. The feeding behavior of a predator is a consequence
of encountering prey. The mass-specific encounter rate (year$^{-1}$)
$E_{i}$ of a predator $i$ is:
\begin{equation}
E_{i} = V_{i}  \sum_{j} \theta_{i,j} B_j,
\end{equation}
where $\theta_{i,j}$
denotes the feeding preference of a predator $i$ on a prey $j$ (see
Section **Predation**). $B_j$ represents the biomass of a prey $j$ including
zooplankton, benthos, or fish. Therefore, the $\sum_{j} \theta_{i,j} B_j$
represents the biomass of all prey available to a predator.

## Reproduction and growth

When the assimilated energy is still positive after meeting the demand of
the basal metabolism, fish can conduct growth and reproduction. The
reproductive rate (year$^{-1}$) of each size class of fish is:
\begin{equation}
\rho_i =
  \begin{cases}
 \psi_i \nu_i, & \text{$ \nu_i > 0 $}   \\
     0, & \text{$ \nu_i \leq 0 $} 
  \end{cases}
\end{equation}
$\psi_i$ is the maturity level (dimensionless) of fish $i$,
describing the proportion of available energy ($\nu_{i}$) used in the
reproduction process. It can be either assigned with constants manually
(setupBasic and setupVertical [@petrik2019bottom; @van2021emergent]) or
by a sigmoid function (setupBasic2 and setupVertical2):
\begin{equation}
\psi_i = \left(1+\left(\frac{m_{\mathrm{c},i}}{m_{\mathrm{mature}}}\right)^{-5} \right)^{-1}
\end{equation}
$m_{\mathrm{mature}}$ is the half-maturation size of a functional type, which
means fish reach 50% maturity level at $m_{\mathrm{mature}}$.
\begin{equation}
m_{\mathrm{mature}} = \eta_{\mathrm{mature}} M
\end{equation}
where $\eta_{\mathrm{mature}}$ is the
coefficient determining the half-maturation size relative to the max
size of a functional type.

The remaining fraction of the available energy $\nu_{i}$ is invested in growth $\gamma_i$: 
\begin{equation}
 \gamma_i =
  \begin{cases}
\frac{ (1 - \psi_i) \nu_i - \mu_i }{1-(1/z)^{1-\mu_i/\kappa_i \nu_i}}, & \text{$ \nu_i > 0 $}   \\
     0, & \text{$ \nu_i \leq 0 $} 
  \end{cases}
\end{equation}
The detail can be found in [@deRoos2008]. $\mu_i$ is the total
mortality including the predation mortality rate ($\mu_{\mathrm{p},i}$),
background mortality rate ($\mu_{\mathrm{p},i}$), and fishing mortality rate
($\mu_{\mathrm{f},i}$): 
\begin{equation}
\mu_i = \mu_{\mathrm{p},i}+\mu_{\mathrm{b},i}+\mu_{\mathrm{f},i}
\end{equation}
All size classes of fish experience a background mortality. The details of
predation and fishing are in the sections below.

## Predation

The second core element of FEISTY, besides the equation for biomass dynamics, is the specification of how each size class interacts via predation. This is specified in the feeding preference matrix (also known as a food-web matrix) $\theta_{i,j}$ where each element is a number between 0 and 1 which denotes how much a fish class $i$ preys on a prey class $j$. The feeding preference function is either based on size preference or derived from size preference coupling with the vertical habitat of each functional group. All of them are combined with additional modifications to account for feeding specializations.

Once the feeding preference is ready, the predation mortality of a prey
$j$ can be calculated.
\begin{equation}
\mu_{\mathrm{p},j} = \sum_i  \frac{V_i \theta_{i,j}  B_i}{E_i+C_{\mathrm{max},i}} C_{\mathrm{max},i}
\end{equation}

In the vertical distribution setups, $\theta_{i,j}$ is the product of
size-based preference ($\theta_{\mathrm{s},i,j}$) and vertical overlap ($\theta_{\mathrm{v},i,j}$)
\begin{equation}
\theta_{i,j} = \theta_{\mathrm{s},i,j} \cdot\theta_{\mathrm{v},i,j} 
\label{eq:verttheta}
\end{equation}
The calculation of $\theta_{\mathrm{s},i,j}$ follows Eq. \ref{eq:errorpreference} in setupVertical and Eq. \ref{eq:lognormalpreference} in setupVertical2. The detailed description of $\theta_{\mathrm{v},i,j}$ in the Section **Vertical overlap**.

### Size preference
In the non-vertical distribution version (`setupBasic` and `setupBasic2`)
$\theta_{i,j}$ refers to the feeding preference based on the size
preference. In vertical distribution versions, it is named $\theta_{s,i,j}$ for differentiation purposes. The value of $\theta_{i,j}$ can be assigned manually
(setupBasic, see Table 2 in [@petrik2019bottom]). It also can be
calculated by following functions either based on the log-normal
distribution:

\begin{equation}
 \theta_{i, j} =
  \begin{cases}
\exp\left( -\frac{\left(\log\left(\frac{m_{\mathrm{c},i}}{\beta \cdot m_{\mathrm{c},j}}\right)\right)^2}{(2 \cdot \sigma)^2} \right), & \text{$ m_{i} > m_{j} $}   \\
     0, & \text{$ m_{i} \leq m_{j} $} 
  \end{cases}
\label{eq:lognormalpreference}
\end{equation}

or based on the error function [@van2021emergent]:
\begin{equation}
\theta_{i, j} = \frac{\sqrt{\frac{\pi}{2}} \cdot \sigma \cdot \left( \text{erf}\left(\frac{\log(m_{\mathrm{u},j}) - \log\left(\frac{m_{\mathrm{c},i}}{\beta}\right)}{\sqrt{2} \cdot \sigma}\right) - \text{erf}\left(\frac{\log(m_{\mathrm{l},j}) - \log\left(\frac{m_{\mathrm{c},i}}{\beta}\right)}{\sqrt{2} \cdot \sigma}\right) \right)}{\log(m_{\mathrm{u},j}) - \log(m_{\mathrm{l},j})}
\label{eq:errorpreference}
\end{equation}
$\beta$ is preferred predator-prey mass ratio, and $\sigma$ is the
size preference width for feeding. The size-preference function
selection and the values of $\beta$ and $\sigma$ can be defined by the
function `paramSizepref()`.

### Vertical overlap
Concise introduction...

water column discretization
\begin{equation}
z_{\mathrm{\zeta}} =  0+\zeta, \hspace{1.5cm}  \zeta\in[0,z_{\mathrm{b}}]
\end{equation}
where $\zeta$ is each depth of a water column (integer value), ranging from $0$ (surface) to $z_{\mathrm{bottom}}$ (sea floor).


$z_{\mathrm{dvm}}$ is the representative depth where there is max biomass when functional types or size classes conduct the diel vertical migration.

\begin{equation}
  z_{\mathrm{dvm}} =
  \begin{cases}
     z_{\mathrm{photc}} + 500, & \text{ $z_{\mathrm{bottom}} \geq z_{\mathrm{photic}} + 500$ } \\
     z_{\mathrm{bottom}}, & \text{ $ z_{\mathrm{photic}} + 500 > z_{\mathrm{bottom}} > z_{\mathrm{shelf}} $ } \\
     0, & \text{$ z_{\mathrm{bottom}} \leq z_{\mathrm{shelf}} $ }      
  \end{cases}
\label{eq:zdvm}
\end{equation}

For demersal fish, their are different due to living habits
\begin{equation}
  z_{\mathrm{dvmdem}} =
  \begin{cases}
     z_{\mathrm{dvm}}, & \text{ $ z_{\mathrm{bottom}} - z_{\mathrm{dvm}} < 1200 $ } \\
     z_{\mathrm{bottom}} - 1200, & \text{ $ 1200 \leq z_{\mathrm{bottom}} - z_{\mathrm{dvm}} <1500 $ } \\
     z_{\mathrm{bottom}}, & \text{ $ z_{\mathrm{bottom}} - z_{\mathrm{dvm}} \geq 1500 $ }      
  \end{cases}
\label{eq:zdvmdem}
\end{equation}

Width of the vertical distribution of each organism $\omega_i$ including all resources and fish. 

\begin{equation}
  \omega_i = \omega_0 + \tau \cdot \log_{10}\left(\frac{m_{\mathrm{c},i}}{m_{\mathrm{c},0}}\right)
\end{equation}

where $\omega_0$ is the baseline width of vertical distribution and $\tau$ is the width-increasing factor of vertical distribution. $m_{\mathrm{c},0}$ denotes the minimum geometric mean size within all organisms in the simulation (typically small mesozooplankton). Note, for benthic resources, $\omega_i = \omega_0$ to make them stay nearly at the bottom.

a function to generate vertical distributions (a normal distribution)

\begin{equation}
  \theta_{\mathrm{\zeta},\mathrm{x},i} = \frac{1}{\sqrt{2\pi\omega_i^2}} \cdot \exp\left(-\frac{(z_{\mathrm{\zeta}} - z_{\mathrm{loc},\mathrm{x},i})^2}{2\omega_i^2}\right)\\
  \label{eq:vertdist1}
\end{equation}

\begin{equation}
  \theta_{\mathrm{\zeta},\mathrm{x},i} = \frac{\theta_{\mathrm{\zeta},\mathrm{x},i}}{\sum\limits_{\mathrm{\zeta}} \theta_{\mathrm{\zeta},\mathrm{x},i}}
  \label{eq:vertdist2}
\end{equation}

x is either day or night. $z_{\mathrm{loc},\mathrm{x},i}$ is the representative depth that the maximum biomass is. Some functional types or size classes have two representative depths $z_{\mathrm{loc},\mathrm{x},i}$. Consequently, they need to be calculated twice (Eq. \ref{eq:vertdist1} and \ref{eq:vertdist2}) and the vertical distribution is the averaged value, which shows a bimodal shape of the vertical distribution. The description of $z_{\mathrm{loc},\mathrm{x},i}$ of different functional types and size classes can be found in ().

Predator-prey vertical overlap

The less value between vertical distribution values of a specific predator $i$ and a prey $j$ at depth $\zeta$ at daytime or nighttime $x$ $\min(\theta_{\mathrm{\zeta},\mathrm{x},i}, \theta_{\mathrm{\zeta},\mathrm{x},j})$ represents their vertical overlap level. The depth-integration gives the synthetic vertical overlap value of predator $i$ to a prey $j$ at day or night $\theta_{\mathrm{v},\mathrm{x},i,j}$:

\begin{equation}
  \theta_{\mathrm{v},\mathrm{x},i,j} = \sum\limits_{\mathrm{\zeta}}\min(\theta_{\mathrm{\zeta},\mathrm{x},i},\theta_{\mathrm{\zeta},\mathrm{x},j})
\end{equation}

The light conditions of a location where visual predators stay in a water column influence their prey-capturing performances. Small pelagics and large pelagics are visual predators whose predation ability is better in light-rich waters during the day and worse in dark conditions such as night or the twilight zone. These traits are reflected by the modified vertical overlap values. Therefore, according to habitats at day and night (Table \ref{tab:vertloc}) the vertical overlap data is further modified by multiplying the visual scaling factor $\theta_{\mathrm{visual}}$:

\begin{equation}
  \theta_{\mathrm{v},x,i,j} = \theta_{\mathrm{v},x,i,j} \cdot \theta_{\mathrm{visual}} .
\end{equation}

All small pelagics and small- and medium-size class [^1] large pelagics always stay at the surface regardless of day and night, so their daytime vertical overlap on all prey ($\theta_{\mathrm{v},day,i,j}$) is enhanced ($\theta_{\mathrm{visual}}=1.5$). Correspondingly, their nighttime vertical overlap ($\theta_{\mathrm{v},night,i,j}$) is decreased ($\theta_{\mathrm{visual}}=0.5$).

[^1]: small-, medium-, and large-size classes of fish are distinguished by comparison between the geometric mean mass value ($m_{\mathrm{c},i}$) and boundary mass value ($m_{\mathrm{medium}}$ or $m_{\mathrm{large}}$). Small-size class: $m_{\mathrm{c},i} < m_{\mathrm{medium}}$.
Medium-size class: $m_{\mathrm{medium}} \leq m_{\mathrm{c},i} \leq m_{\mathrm{large}}$.
Large-size class: $m_{\mathrm{c},i} > m_{\mathrm{large}}$.

Half of large-size class large pelagics stay at the twilight zone ($z_{\mathrm{dvm}}$) at daytime, so their vertical overlap at daytime ($\theta_{\mathrm{v},day,i,j}$) on all mesopelagic fish and bathypelagic fish is reduced ($\theta_{\mathrm{visual}}=0.5$).

Ultimately, the total vertical overlap is the average value of day and night vertical overlap values.

\begin{equation}
  \theta_{\mathrm{v},i,j} = \frac{\theta_{\mathrm{v},\mathrm{day},i,j}+\theta_{\mathrm{v},\mathrm{night},i,j}}{2}
  \label{eq:}
\end{equation}

This can be used for the calculation of feeding preference ($\theta_{i,j}$) in Eq. \ref{eq:verttheta}. Note $\theta_{i,j}$ still needs to be further modified according to feeding behaviours (see Section **Modification**).


put in supplementary?
**Zooplankton resources**\
Zooplankton resources (small and large mesozooplankton) are supposed to be divided into two types in terms of whether they can conduct the diel vertical migration if water column conditions allow. During the daytime, half of them move to deep water to avoid predation ($z_{\mathrm{loc},\mathrm{day},i} = z_{\mathrm{dvm}}$). Another half is in the surface water ($z_{\mathrm{loc},\mathrm{day},i} = 0$). At nighttime, they stay at the surface ($z_{\mathrm{loc},\mathrm{x},i} = 0$).

**Benthic resources**\
Benthos is benthic-living ($z_{\mathrm{loc},\mathrm{day},i} = z_{\mathrm{loc},\mathrm{night},i} = z_{\mathrm{bottom}}$). To ensure they stay close to the sea floor, their vertical distribution width is kept as the baseline value $\omega_i=\omega_0$.

**Small pelagics**\
They always stay in the surface water ($z_{\mathrm{loc},\mathrm{day},i} = z_{\mathrm{loc},\mathrm{night},i} = z_{\mathrm{bottom}}$).

**Mesopelagics**\
Mesopelagic fish stay at the midwater during daytime ($z_{\mathrm{loc},\mathrm{day},i} = z_{\mathrm{dvm}}$). At night, they migrate to the surface ($z_{\mathrm{loc},\mathrm{night},i} = 0$).

**Large pelagics**\
During the daytime, Large pelagics perform differently according to their size. The small- and medium-size classes are at the surface ($z_{\mathrm{loc},\mathrm{day},i} = 0$). The large-size classes are divided into two groups: half of them are always in the surface water ($z_{\mathrm{loc},\mathrm{day},i} = 0$), and half in midwater ($z_{\mathrm{loc},\mathrm{day},i} = z_{\mathrm{dvm}}$). 
They all move to the surface during night ($z_{\mathrm{loc},\mathrm{night},i} = 0$)

**Bathpelagics**\
All bathypelagic fish stay at the dvm depth during daytime ($z_{\mathrm{loc},\mathrm{day},i} = z_{\mathrm{dvm}}$). At night, the small- and medium-size classes are always at the surface ($z_{\mathrm{loc},\mathrm{night},i} = 0$). Large-size classes are in midwater ($z_{\mathrm{loc},\mathrm{night},i} = z_{\mathrm{dvm}}$).

**Demersals**\
During daytime, small demersals are at the surface ($z_{\mathrm{loc},\mathrm{day},i} = 0$); medium demersals are at the bottom ($z_{\mathrm{loc},\mathrm{day},i} = z_{\mathrm{bottom}}$); large demersals are at midwater ($z_{\mathrm{loc},\mathrm{day},i} = z_{\mathrm{dvmdem}}$).
At night, small demersal fish are at the surface ($z_{\mathrm{loc},\mathrm{night},i} = 0$). Medium and large demersal fish are at the bottom ($z_{\mathrm{loc},\mathrm{night},i} = z_{\mathrm{bottom}}$).

\begin{table}[htbp]

\centering
\caption{ Biomass representative depth for each size class $z_{\mathrm{loc},\mathrm{x},i}$ at day and night. $z_{\mathrm{dvm}}$ and $z_{\mathrm{dvmdem}}$ can be found in Eq. \ref{eq:zdvm} and \ref{eq:zdvmdem}.}
\label{tab:vertloc}

\begin{tabular}{ l l l p{2cm} l l p{2cm}}
\hline
 & \multicolumn{3}{l}{Day} & \multicolumn{3}{l}{Night} \\
   \cline{2-7} 
Resources\\
\hline
Zooplankton$^a$ & \multicolumn{3}{l}{0 and $z_{\mathrm{dvm}}$} & \multicolumn{3}{l}{0} \\
Benthos & \multicolumn{3}{l}{$z_{\mathrm{bottom}}$} & \multicolumn{3}{l}{$z_{\mathrm{bottom}}$} \\
   \cline{2-7}
&\\   
Fish & Small & Medium & Large & Small & Medium & Large \\
\hline
Small pelagic fish & 0 & 0 & / & 0 & 0 & / \\
Mesopelagic fish & $z_{\mathrm{dvm}}$ & $z_{\mathrm{dvm}}$ & / & 0 & 0 & / \\
Large pelagic fish & 0 & 0 & 0 and $z_{\mathrm{dvm}}$ & 0 & 0 & 0 \\
Bathypelagic fish & $z_{\mathrm{dvm}}$ & $z_{\mathrm{dvm}}$ & $z_{\mathrm{dvm}}$ & 0 & 0 & $z_{\mathrm{dvm}}$ \\
Demersal fish & 0 & $z_{\mathrm{bottom}}$ & $z_{\mathrm{dvmdem}}$$^e$ & 0 & $z_{\mathrm{bottom}}$ & $z_{\mathrm{bottom}}$$^e$ \\

\hline
\multicolumn{7}{l}{\footnotesize $^a$ Zooplankton include small and large mesozooplankton} \\
\multicolumn{7}{l}{\footnotesize $^b$ ....}\\
\multicolumn{7}{p{\dimexpr\linewidth-2\tabcolsep}}{\footnotesize $^e$ If the water column is shallower than the photic zone depth ($z_{\mathrm{bottom}} < z_{\mathrm{photic}}$), large demersal fish migrate over the water column (two  $z_{\mathrm{loc},\mathrm{x},i}$ for each day and night: $z_{\mathrm{dvmdem}}$ and $z_{\mathrm{bottom}}$), resulting a normal distribution centered at the middle of the water column. In such cases, $z_{\mathrm{dvmdem}}=0$.}

\end{tabular}
\end{table}


### Modifications

Basic2

In practice, the feeding preference setting is more complex, since it plays a vital role in the coexistence of various functional types. when the feeding preference $\theta_{i,j}$ is initially calculated as a function (e.g., Eq. \ref{eq:lognormalpreference}), sometimes it needs to be revised or corrected manually according to specific rules, such as cannibalism, habitats, feeding habits, and visibility. Here I introduce how the feeding preference $\theta_{i,j}$ is further processed in setupBasic2.

Forage fish and large pelagic fish live in the pelagic zone during their whole lifetime. Demersal fish habitats are different in terms of their sizes and water depth. Small demersal fish are pelagic status while medium demersal fish are benthic-living. Pelagic-living organisms do not interact with benthic-living organisms and vice versa.

**Forage fish**\
The feeding preference from forage fish and large pelagic fish to benthic resources and medium demersal fish are corrected to 0.

**Large pelagic fish**\
The feeding preference from large pelagic fish to benthic resources and medium demersal fish is corrected to 0.
Large pelagic fish have a reduced feeding preference for forage fish ($\theta_{\mathrm{A}} \cdot \theta_{i,j}$).

**Demersal fish**\
The feeding preference from small demersal fish to benthic resources is corrected to 0.\
Medium demersal fish only feed on benthos and themselves (cannibalism). Therefore, their feeding preference on zooplankton and all fish excluding themselves is corrected to 0.\
In shallow water ($<~200$ m), large demersal fish swim over the water column, meaning they can eat both pelagic and benthic organisms. Their feeding preference on forage fish was down-regulated: $\theta_{\mathrm{A}} \cdot \theta_{\mathrm{D}} \cdot \theta_{i,j}$. Their feeding preference on large pelagic fish was down-regulated: $\theta_{\mathrm{D}} \cdot \theta_{i,j}$.\
When water is deep ($>~200$ m), large demersal fish is fully benthic-living. So the feeding preference of large demersals on all pelagic prey is corrected to 0, including forage fish, large pelagic fish, zooplankton, and small demersal fish. They only can feed on benthos, medium demersals, and themselves.

**Vertical**

It is assumed all pelagic functional types (forage fish, mesopelagics, large pelagics, and bathypelagics) and small demersal fish (pelagic-living) do not consume benthos ($\theta_{i,j}=0$). Also, their feeding preference on medium demersal fish (benthic-living) is reduced by multiplying 0.25 ($\theta_{i,j}=\theta_{i,j} \cdot 0.25$).
Medium and large demersal fish are assumed not to eat zooplankton ($\theta_{i,j}=0$).
To maintain the coexistence between large pelagic predators and small fish, some benefits in predation avoidance are assigned to medium-size forage fish and medium-size mesopelagic fish by a similar method in [@petrik2019bottom].
Large-size classes of pelagic-living functional fish groups (large pelagic fish, bathypelagic fish, and demersal fish) have reduced feeding preference on medium-size forage fish and medium-size mesopelagic fish ($\theta_{i,j}=\theta_{i,j} \cdot 0.5$). 

## Fishing mortality

The fishing mortality rate $\mu_{\mathrm{f},i}$ of a particular size class of
fish $i$ can be either determined by constant values or by a fishing
selectivity function [@andersen2019fish, Chapter 5]:
\begin{equation}
\mu_{\mathrm{f},i}=\psi_{\mathrm{f},i}F
\label{eq:fishing}
\end{equation}
where $F$ is the baseline fishing mortality rate (year$^{-1}$) of a functional type of
fish. $\psi_{\mathrm{f},i}$ denotes a trawl-based fishing selectivity following
a sigmoid function:
\begin{equation}
\psi_{\mathrm{f},i} = \left(1+\left(\frac{m_{\mathrm{c},i}}{m_{\mathrm{fishing}}}\right)^{-3} \right)^{-1}
\end{equation}
where $m_{\mathrm{fishing}}$ indicates the fish with this size is under 50% harvesting rate.
\begin{equation}
m_{\mathrm{fishing}}=\eta_{\mathrm{F}} M
\end{equation}
where $\eta_{\mathrm{F}}$ controls the weight of fish with a 50% harvesting rate relative to the max weight of the functional type.
The fishing mortality rate can be assigned by the function `setFishing()`.

## Temperature effects
The temperature effects on the mass-specific maximum consumption rate $C_{\mathrm{max},i}$, the mass-specific clearance rate $V_{i}$, and the mass-specific metabolic rate $M_i$ (Eq. \ref{eq:maxconsump}, \ref{eq:clearance}, \ref{eq:metabolism}) are based on the use of the $Q_{10}$ coefficient, which describes the exponential variation of rates every 10\textdegree{}C.

The general equation for the temperature scaling factor $k$ is:
\begin{equation}
k = Q_{10}^{\frac{T-T_{\mathrm{ref}}}{10}} \label{eq:Tscfac}
\end{equation}
where $T_{\mathrm{ref}}$ is the reference temperature and $T$ is the environment temperature.
According to the different functional types of fish and their sizes, fish habitats change. For fish staying in the pelagic zone, $T=T_{\mathrm{p}}$ (e.g., all forage fish); for fish always in the benthic zone $T=T_{\mathrm{b}}$ (e.g., medium-size demersal fish). Through introducing different $Q_{10}$ coefficients (Table \ref{tab:defaultparam}), various temperature scaling factors $k$ can be obtained. $k_{\mathrm{T}}$ is the temperature scaling factor for $C_{\mathrm{max},i}$, and $V_{i}$; $k_{\mathrm{TM}}$ is the temperature scaling factor for $M_i$.

**setupBasic and setupBasic2**

In `setupBasic` and `setupBasic2`, there are three functional types of fish: forage fish (small pelagic fish), large pelagic fish, and demersal fish. Forage fish and large pelagics are always in the pelagic water, so the $T_{\mathrm{p}}$ is consistently applied. Demersal fish habitats change according to size. Small demersal is in a pelagic status ($T_{\mathrm{p}}$). Medium demersals live at the bottom ($T_{\mathrm{b}}$). Large demersals also stay in the bottom if the water is deep ($>~200$ m). However, in shallow water ($<~200$ m), due to their better swimming abilities, the large demersals migrate over the water column for feeding. In code implementation, temperature effects on biological rates are done by the function `paramTeffect()`. Note this function only works on non-vertical distribution setups, i.e., `setupBasic` and `setupBasic2`. Moreover, to better describe the temperature effects on large demersals, the effective temperature is introduced (see Section **Real-time effective temperature**).

**setupVertical**

In setupVertical, fish have a new trait axis of vertical distribution. Temperature effects on physiological rates of each size class are based on where fish stay in a water column (environmental temperature). Therefore the total vertical distribution data needs to be calculated initially:

\begin{equation}
  \theta_{\mathrm{\zeta},i} = \frac{\theta_{\mathrm{\zeta},\mathrm{day},i}+\theta_{\mathrm{\zeta},\mathrm{night},i}}{2}
\end{equation}

Then the temperature scaling factor of each size class in a discretized water column can be obtained according to their vertical distribution:

\begin{equation}
k_{\mathrm{\zeta},i} = \theta_{\mathrm{\zeta},i} \cdot Q_{10}^{\frac{T_{\mathrm{\zeta}}-T_{\mathrm{ref}}}{10}}
\end{equation}

where the water column temperature profile ranging from the surface (0 m) to the bottom, which can be obtained from observational data products or earth system model outputs. Finally, the scaling factor is integrated over the vertical distribution.

\begin{equation}
k_{i} = \sum\limits_{\mathrm{\zeta}} k_{\mathrm{\zeta},i}
\end{equation}

$k_{i}$ can be used in  temperature effects on physiological rates Eq. \ref{eq:maxconsump}, \ref{eq:clearance}, \ref{eq:metabolism}. The implementation is hard-coded, and embedded in the function `setupVertical()`.



**setupVertical2**

To simplify the temperature input, three temperature inputs ($T_{\mathrm{p}}$, $T_{\mathrm{m}}$, $T_{\mathrm{b}}$) are required rather than the water column temperature profile in setupVertical2. The effective temperature of different size classes of each functional type are the averaged values of temperatures of their approximate vertical positions of day ($T_{\mathrm{day}}$) and night ($T_{\mathrm{night}}$).
\begin{equation}
T_{\mathrm{e}} = \frac{T_{\mathrm{day}}+T_{\mathrm{night}}}{2}
\end{equation}

Note this $T_{\mathrm{e}}$ is different from the one in the Section **Real-time effective temperature**. Then $T_{\mathrm{e}}$ is taken into Eq. \ref{eq:Tscfac} as $T$, and so the temperature-dependent physiological rates (Eq. \ref{eq:maxconsump}, \ref{eq:clearance}, \ref{eq:metabolism}) are updated. The implementation is hard-coded in the function `setupVertical2()`. 

**Small pelagics**\
They always stay in the pelagic water ($T_{\mathrm{day}}=T_{\mathrm{night}}=T_{\mathrm{p}}$).

**Mesopelagics**\
At daytime, where mesopelagic fish stay depends on the water column depth and photic conditions:
\begin{equation}
 T_{\mathrm{day}} =
  \begin{cases}
     T_{\mathrm{m}}, & \text{$ z_{\mathrm{dvm}} \neq z_{\mathrm{bottom}} $ and $ z_{\mathrm{dvm}} \neq 0 $ } \\
     T_{\mathrm{b}}, & \text{$ z_{\mathrm{dvm}} = z_{\mathrm{bottom}} $} \\
     T_{\mathrm{p}}, & \text{$ z_{\mathrm{dvm}} = 0 $}      
  \end{cases}
\label{eq:xxxxxxxx}
\end{equation}
During night time, they are in the pelagic water ($T_{\mathrm{night}}=T_{\mathrm{p}}$).

**Large pelagics**\
The large-size classes of large pelagic fish are split into two groups: half of them are always in the pelagic zone, and the habitat of the other half depends on the water column conditions. So their daytime temperature could be the average of two environmental temperatures. If the water column does not support the existence of dvm they all stay in the pelagic zone. 

\begin{equation}
 T_{\mathrm{day}} =
  \begin{cases}
     \frac{T_{\mathrm{m}}+T_{\mathrm{p}}}{2}, & \text{$ z_{\mathrm{dvm}} \neq z_{\mathrm{bottom}} $ and $ z_{\mathrm{dvm}} \neq 0 $ } \\
     \frac{T_{\mathrm{b}}+T_{\mathrm{p}}}{2}, & \text{$ z_{\mathrm{dvm}} = z_{\mathrm{bottom}} $} \\
     T_{\mathrm{p}}, & \text{$ z_{\mathrm{dvm}} = 0 $}      
  \end{cases}
\label{eq:xxxxxxx}
\end{equation}

All the large pelagics in non-large sizes (small and medium) are in pelagic water the during daytime ($T_{\mathrm{day}}=T_{\mathrm{p}}$).\
During nighttime, all of them regardless of size are in the pelagic water ($T_{\mathrm{night}}=T_{\mathrm{p}}$).

**Bathypelagics**\
Bathypelagic fish stay at the dvm depth, bottom, or pelagic zone, depending on the water column depth and photic conditions at daytime:
\begin{equation}
 T_{\mathrm{day}} =
  \begin{cases}
     T_{\mathrm{m}}, & \text{$ z_{\mathrm{dvm}} \neq z_{\mathrm{bottom}} $ and $ z_{\mathrm{dvm}} \neq 0 $ } \\
     T_{\mathrm{b}}, & \text{$ z_{\mathrm{dvm}} = z_{\mathrm{bottom}} $} \\
     T_{\mathrm{p}}, & \text{$ z_{\mathrm{dvm}} = 0 $} 
  \end{cases}
\label{eq:xxxxxxx2}
\end{equation}

At nighttime, small and medium bathypelagics are in the pelagic water ($T_{\mathrm{night}}=T_{\mathrm{p}}$), but the habitats of large bathypelagics varies with water column conditions: 
\begin{equation}
 T_{\mathrm{night}} =
  \begin{cases}
     T_{\mathrm{m}}, & \text{$ z_{\mathrm{dvm}} \neq z_{\mathrm{bottom}} $ and $ z_{\mathrm{dvm}} \neq 0 $ } \\
     T_{\mathrm{b}}, & \text{$ z_{\mathrm{dvm}} = z_{\mathrm{bottom}} $} \\
     T_{\mathrm{p}}, & \text{$ z_{\mathrm{dvm}} = 0 $}  
  \end{cases}
\label{eq:xxxxxx}
\end{equation}

**Demersals**\
Small demersals are pelagic-living ($T_{\mathrm{day}}=T_{\mathrm{night}}=T_{\mathrm{p}}$); medium demersals are benthic-living ($T_{\mathrm{day}}=T_{\mathrm{night}}=T_{\mathrm{b}}$).
Large demersal fish habitats vary according to the water column conditions.

\begin{equation}
 T_{\mathrm{day}} =
  \begin{cases}
     T_{\mathrm{m}}, & \text{$ (z_{\mathrm{bottom}} - z_{\mathrm{dvm}}) < 1500 $ and $ z_{\mathrm{bottom}} \geq z_{\mathrm{photic}} $} \\
     T_{\mathrm{b}}, & \text{$ (z_{\mathrm{bottom}} - z_{\mathrm{dvm}}) \geq 1500 $ } \\
     \frac{T_{\mathrm{b}}+T_{\mathrm{p}}}{2}, & \text{$ z_{\mathrm{bottom}} < z_{\mathrm{photic}} $} 
  \end{cases}
\label{eq:xxxxxx2}
\end{equation}

\begin{equation}
 T_{\mathrm{night}} =
  \begin{cases}
     T_{\mathrm{b}}, & \text{$ z_{\mathrm{bottom}} \geq z_{\mathrm{photic}} $}  \\
     \frac{T_{\mathrm{b}}+T_{\mathrm{p}}}{2}, & \text{$ z_{\mathrm{bottom}} < z_{\mathrm{photic}} $} 
  \end{cases}
\label{eq:xxxxxx3}
\end{equation}

### Real-time effective temperature
Following [@petrik2019bottom], in shallow water ($<~200$ m) the large demersal fish ($m_{\mathrm{c},i}>250$ gWW as default)
migrate vertically within a day rather than staying at the bottom constantly. They are assumed to spend a fraction of time $\lambda$ in the pelagic zone and the rest of time $1-\lambda$ at the bottom according to the abundance of prey in these two zones.
\begin{equation}
\lambda = \frac{B_{\mathrm{pelprey}}}{B_{\mathrm{allprey}}}
\end{equation}
where $B_{\mathrm{pelprey}}$ denotes the total biomass of pelagic prey for large demersal fish, $B_{\mathrm{allprey}}$ is the total biomass of all prey for large demersal fish. A simple case can be found in Eq. 15 in [@petrik2019bottom].\
Therefore, the temperature for large demersals is defined based on their time spent in the pelagic zone and benthic zone, which is called effective temperature:
\begin{equation} 
T_{\mathrm{e}} = T_{\mathrm{p}} \cdot \lambda + T_{\mathrm{b}} \cdot (1 - \lambda)
\end{equation}
$T_{\mathrm{e}}$ is updated each time step during the time integration, along with the temperature-dependent biological rates, which are handled by the function `updateET()`. In code implementation, `updateET()` is called every time step in `derivativesFEISTYR()`. The effective temperature scheme is forced turned on in `setupBasic()` [@petrik2019bottom]; it is an option in `setupBasic2()`.


## Setup of the size spectrum grid

The fish size span of a functional type is logarithmically discretized
into $n$ continuous size bins. Each size bin shares the same ratio $z$
between the upper boundary size and lower boundary size:
\begin{equation}
z = \exp \left( \frac{\ln (M) - \ln (M_{0})}{n} \right)
\end{equation} 
where $M_{0}$ and $M$ are the smallest and largest fish in a functional type (boundary size). There are $n+1$ boundaries of $n$ size bins ($m_{\mathrm{b},i}$), including all lower boundary sizes ($m_{\mathrm{l},i}$) and upper boundary sizes ($m_{\mathrm{u},i}$). 
\begin{equation}
m_{\mathrm{b},i} =  \exp( \ln(M_{0}) + (i-1) \ln(z)), \hspace{1.5cm}  i\in[1,n+1]
\end{equation} 
\begin{equation}
m_{\mathrm{l},i} =  m_{\mathrm{b},i}, \hspace{5.5cm}  i\in[1,n]
\end{equation}
\begin{equation}
m_{\mathrm{u},i} =  m_{\mathrm{b},i+1}, \hspace{5.1cm}  i\in[1,n]
\end{equation}
The geometric mean size of each size class $m_{i}$ is:
\begin{equation}
m_{i} =  \exp ( \ln(m_{\mathrm{l},i}) + 0.5(\ln(z)) ), \hspace{2.2cm}  i\in[1,n]
\end{equation}
which can be comprehensively used for calculations, for instance,
physiological rates and size-based feeding preference.\
The size spectrum generation is done by calling the function
`paramAddGroup()`. Also, see the source code of `makeGrid()`.

\newpage

# Default parameters

\begin{table}[htbp]

\centering
\caption{Main parameters of FEISTY}
\label{tab:defaultparam}

\begin{tabular}{lp{8cm}lp{1cm}lp{1cm}lp{1cm}lp{1cm}l}
\hline
Symbol & Description & \multicolumn{4}{c}{Value} & Unit \\
                         \cline{3-6}
       &             & \multicolumn{1}{c}{B1} & \multicolumn{1}{c}{B2} & \multicolumn{1}{c}{V1} & \multicolumn{1}{c}{V2} & \\
\hline
$a_c$ & Intercept for mass-specific maximum consumption rate & \multicolumn{4}{c}{20} & $g^{-b_{\mathrm{c}}}$yr$^{-1}$ \\
$b_c$ & Exponent for mass-specific maximum consumption rate & \multicolumn{4}{c}{-0.25} & / \\
$a_e$ & Intercept for mass-specific clearance rate & \multicolumn{4}{c}{70} & $m^2 g^{-b_{\mathrm{e}}-1}$yr$^{-1}$ \\
$b_e$ & Exponent for mass-specific clearance rate & \multicolumn{4}{c}{-0.2} & / \\
$a_m$ & Intercept for mass-specific metabolism rate & \multicolumn{2}{c}{4.015} & \multicolumn{2}{c}{0.2*$a_{\mathrm{c}}$} & $g^{-b_{\mathrm{m}}}$yr$^{-1}$ \\
$b_m$ & Exponent for mass-specific metabolism rate & \multicolumn{4}{c}{-0.175} & / \\
$\epsilon_{\alpha}$ & Assimilation efficiency & \multicolumn{4}{c}{0.7} & / \\
$\epsilon_{r}$ & Reproduction efficiency & \multicolumn{4}{c}{0.01} & / \\
$\mu_b$ & Background mortality & \multicolumn{4}{c}{0.1} & yr$^{-1}$ \\
$F$ & Baseline fishing mortality rate & /$^e$ & \multicolumn{3}{c}{0} & yr$^{-1}$ \\
$\eta_{mature}$ & half-maturation size coefficient & /$^c$ & \multicolumn{3}{c}{0.25} & / \\
$\eta_{fishing}$ & half-harvesting size coefficient & /$^d$ & \multicolumn{3}{c}{0.05} & / \\
$\theta_A$ & Large fish preference on forage fish$^b$ & \multicolumn{2}{c}{0.5} & / & / & / \\
$\theta_D$ & Large demersal fish preference on pelagic prey & \multicolumn{2}{c}{0.75} & / & / & / \\
$aaa$ & xxx & 0.1 & 0.2 & 0.3 & 0.4 & gWW \\
$T_{ref}$ & reference temperature & \multicolumn{4}{c}{10} & \textdegree{}C \\
$Q_{10}$ & Rate of change for every 10\textdegree{}C increase for clearance rate and maximum consumption & \multicolumn{4}{c}{1.88} & / \\
$Q_{10m}$ & Rate of change for every 10\textdegree{}C increase for metabolism & \multicolumn{2}{c}{2.35} & \multicolumn{2}{c}{1.88} & / \\
$aaa$ & xxx & 0.1 & 0.2 & 0.3 & 0.4 & gWW \\
$\beta$ & Preferred predator:prey mass ratio & / & \multicolumn{3}{c}{400} & / \\
$\sigma$ & Width of size preference for feeding & / & \multicolumn{3}{c}{1.3} & / \\
$aaa$ & Continental shelf depth & / & / & \multicolumn{2}{c}{250} & m \\
$aaa$ & Photic zone depth & / & / & \multicolumn{2}{c}{150} & m \\
$m_{\mathrm{medium}}$ & boundary size of small/medium fish class & \multicolumn{4}{c}{0.5} & gww \\
$m_{\mathrm{large}}$ & boundary size of medium/large fish class  & \multicolumn{4}{c}{250} & gww \\

\hline
\multicolumn{7}{l}{\footnotesize $^a$ B1: setupBasic1, B2: setupBasic2, V1: setupVertcal1, V2: setupVertcal2.} \\
\multicolumn{7}{l}{\footnotesize $^b$ In B1, $\theta_{\mathrm{A}}$ only poses on medium forage fish (the second size class).
                                      In B2, $\theta_{\mathrm{A}}$ works on all forage fish.} \\
\multicolumn{7}{l}{\footnotesize $^e$ In B1, Eq. \ref{eq:fishing} does not apply. $\mu_{f,i}$ are constant values: Small fish 0 yr$^{-1}$, Medium fish 0.03 yr$^{-1}$, Large fish 0.3 yr$^{-1}$.}\\

\end{tabular}
\end{table}

# Examples

## The structure of main parameters

**FESITY** includes four setups which each specifies the available functional groups and their parameters:

-   setupBasic creates a basic three-species setup as described in
    Petrik et al (2019) 
-   setupBasic2 creates the same three-species setup as setupBasic(), but
    generalised to: more realistic sizes, generalized size-based
    feeding, and the possiblity of more then 3 size groups in each group. (ref)
-   setupVertical makes a basic four-species setup that distinguishes
    between visual and twilight predators and that includes vertical
    distribution of zooplankton  (ref)
-   setupVertical2 is the same as setupVertical but …  (ref) .


## Example

### Fishing mortality
For simplicity, arguments of fishing in **setupbasic()** and **setupVertical()** only allow assigning fishing mortality to all functional types. However, it is feasible to assign fishing mortality for a specific functional type.

```{r}
p=setupVertical2(szprod= 120,lzprod = 120,dfpho=200, depth = 700, 
                 nStages = 9, F=0) # no fishing for all size classes
names(p$mortF)=p$stagenames
df=data.frame(mortF_original=c(p$mortF[p$ix[[1]]],p$mortF[p$ix[[5]]]))
# assign 0.3/year as the baseline fishing mortality to small pelagic fish
p=setFishing(p=p,F=0.2,etaF=0.05,groupidx=c(1))
# assign 0.5/year as the baseline fishing mortality to demersal fish
p=setFishing(p=p,F=0.3,etaF=0.05,groupidx=c(5))
df=cbind(df,data.frame(mortF_new=c(p$mortF[p$ix[[1]]],p$mortF[p$ix[[5]]])))
df

df=data.frame("Stage"=1:length(p$ix[[1]]), "mortF"=p$mortF[p$ix[[1]]],"Groups"="smallPel")
df=rbind(df,data.frame("Stage"=1:length(p$ix[[5]]), "mortF"=p$mortF[p$ix[[5]]],"Groups"="demersals"))
df$Groups=factor(df$Groups,levels=c("smallPel","demersals"))
# plot of fishing mortality of small pelagics and demersals
fig=ggplot(df, aes(x = Stage, y = mortF, color = Groups))+
    geom_line(linewidth = 0.7,alpha=0.9)+
    geom_point(size=1.5,alpha=0.9)+
  labs(x = expression("Stage"), y = expression("Fishing mortality"~(yr^{-1}))) +
  scale_color_manual(values = c("red", "black"),labels=c("Small pelagics","Demersals")) +
  scale_x_continuous(breaks = unique(df$Stage))+
      theme(panel.background = element_rect(fill = "white"),
          panel.border = element_rect(color = "black", fill = NA),
          axis.line = element_line(color = "black"),
          #legend.title = element_blank(),
          legend.key = element_rect(fill = "transparent", color = "transparent"),
          legend.position = "bottom")
  
fig


```

Note customization

```{r}
sim=simulateFEISTY(p = p, tEnd = 200, bCust = T)
plotYieldtime(sim)
```


The model is first run with the default 3-functional group prameters,
created with *setupBasic()*. Then two similar parameter datasets are
created, with rates doubled or halved.

```{r}
p <- setupBasic()
knitr::kable(p$resources, digits=2)
knitr::kable(p$fishes, digits=2)
knitr::kable(p$groups, digits=2)
```

Function *paramAddPhysiology* is used to change the allometric rates:

```{r}
p2 <- paramAddPhysiology(p, ac = 40, am = 8, ae=140)

p3 <- paramAddPhysiology(p, ac = 10, am = 2, ae=35)
```

The model can now be run for all parameter sets; the reulst for the last
20 years are shown.

```{r, fig.width=8, fig.height=8}
out1 <- simulateFEISTY(p=p,  times=seq(0, 200, length.out=1000),bCust=T)
out2 <- simulateFEISTY(p=p2, times=seq(0, 200, length.out=1000),bCust=T)
out3 <- simulateFEISTY(p=p3, times=seq(0, 200, length.out=1000),bCust=T)
# plot(out1, out2, out3, which=5:12, lty=1, lwd=2, subset=time>180)
# plot(out1, out2, out3, which=c("smallZoo", "largeZoo", "smallBenthos", 
#   "totBiomass.smallPel", "totBiomass.largePel",  "totBiomass.Demersals"), 
#   lty=1, lwd=2, subset=time>180)
```




One highlight of the \textit{FEISTY} package is that it allows users to explore and test their new ideas within the model framework, since the package is designed in modular. To customise a new FEISTY model setup, several parameter setup functions are necessary. \texttt{paramInit()} is for initialising the parameter list in R. \texttt{paramAddResource()} and \texttt{paramAddGroup()} are to add resources and functional types into the parameter list. \texttt{paramAddPhysiology()} defines the physiological rates of all functional types including maximum consumption rates, clearance rates, and standard metabolism rates. The size-based feeding preference values can either be assigned by \texttt{paramSizepref()} based on different numerical methods or be assigned manually. Other functions for parameter assignment are optional, such as temperature effects on physiological rates or fishing. Note that some non-general settings cannot be done by internal functions and must be edited manually. Details of how to use these functions can be found in help pages in R.

\newpage

# References

\bibliography{references.bib}
